Neuro V

### 2017-09-06 neuro5.rmd
added table from racgp

-  Refer
-  Admit for initiation or titration of noninvasive ventilation for those with low inspiratory pressure, may prolong survival
-  Riluzole: reduces presynaptic release of Glu, increases short term survival for ALS
-  Symptomatic/supportive measures: trials of anticholinergics
    -  Braces/walker
    -  Physical therapy to prevent contractures
-  Relieve pseudobulbar affect with combination dextromethorphan/quinidine
-  Gastronomy tube if dysphagia is severe
-  Palliative

>>>>

-  Refer
-  Admit for initiation or titration of noninvasive ventilation for those with low inspiratory pressure, may prolong survival
-  Riluzole: reduces presynaptic release of Glu, increases short term survival for ALS
-  Symptomatic/supportive measures: trials of anticholinergics
    -  Braces/walker
    -  Physical therapy to prevent contractures
    -  Mx saliva
    -  Dyspnoea
    -  Constipation
    -  Muscle cramps/spasms/spasticity
    -  Depression, emotional lability
    -  Choking sensation
    -  Panic claustrophobia
-  Relieve pseudobulbar affect with combination dextromethorphan/quinidine
-  Gastronomy tube if dysphagia is severe
-  Palliative
